### 2017-05-17 R/NHTS.Rmd
Updates to NHTS data formatting
Now uses TravelSurvey package.

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
#install.packages(c("ggplot2","dplyr","openssl","httr", "git2r", "devtools", "roxygen2"))
library("ggplot2")
library("devtools")
library("reshape2")
library("plyr")
library("dplyr")
```

@@

@@

>>>>

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
#install.packages(c("ggplot2","dplyr","openssl","httr", "git2r", "devtools", "roxygen2"))
library("ggplot2")
library("devtools")
library("reshape2")
library("plyr")
library("dplyr")
library("TravelSurvey")
```

@@

#saveRDS(NHTS.person, file = "./data/NHTS.person.rds")
#saveRDS(NHTS.trips, file = "./data/NHTS.trips.rds")

@@

```{r TravelSurvey, eval = compute, fig.width = 10, echo = FALSE}

person.df <- with(NHTS.person,{
    data.frame(houseID=HOUSEID, subjectID=PERSONID, sex = SEX, age = AGE, location = HHS)
    })

trip.df <- with(NHTS.trips,{
    data.frame(houseID=HOUSEID, subjectID=PERSONID, duration = TRVL_MIN, mode = AT)
})

person.df <- subset(person.df,apply(person.df,MARGIN=1,FUN=function(x)all(!is.na(x))))
trip.df <- subset(trip.df,apply(trip.df,MARGIN=1,FUN=function(x)all(!is.na(x))))

NHTS.TravelSurvey <- new("TravelSurvey", person = person.df, trip = trip.df)
saveRDS(NHTS.TravelSurvey, file = "~/GHI/R/data/NHTS.TravelSurvey.rds")

NHTS.df <- dplyr::left_join(NHTS.TravelSurvey@person, NHTS.TravelSurvey@trip, by = c("houseID","subjectID"))

NHTS.df <- within(NHTS.df, duration <- ifelse(is.na(duration), 0, duration))
